---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# wordstonumbers   ![codecov.io](https://codecov.io/gh/fsingletonthorn/words_to_numbers/branch/master/graph/badge.svg) ![travis-ci.org](https://travis-ci.org/fsingletonthorn/words_to_numbers.svg?branch=master)


wordstonumbers is an R package for text analysis pre-processing that transforms numbers written in words to numerics (e.g., “one hundred and twenty three thousand” to “123000”). 

## Installation

You can install wordstonumbers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fsingletonthorn/words_to_numbers")
```

## Example

```{r example1}
library(wordstonumbers)

words_to_numbers("ninety-nine red balloons")
```

```{r example2}

words_to_numbers("The answer is forty-two")
```

```{r example3}

words_to_numbers("The PRQ is a twelve-item, four-point Likert scale (from one = Never to four = Very Often) with three sub-scores.")
```

```{r example4}
words_to_numbers("The Library of Babel (by Jorge Luis Borges) describes a library that contains all possible four-hundred and ten page books made with a character set of twenty five characters (twenty two letters, as well as spaces, periods, and commas), with eighty lines per book and forty characters per line.")
```


```{r example5}

words_to_numbers("three hundred billion, one hundred and 79 cats")
```

Note that this function does not currently correctly process magnitudes preceeded by decimals, e.g., 

```{r example6}
words_to_numbers("1.6 Billion")
```

And some other possible values will also not be correctly transformed
```{r example7}
words_to_numbers('three point one four one five nine two six')

```
