---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# wordstonumbers   ![codecov.io](https://codecov.io/gh/fsingletonthorn/words_to_numbers/branch/master/graph/badge.svg) ![travis-ci.org](https://travis-ci.org/fsingletonthorn/words_to_numbers.svg?branch=master)


wordstonumbers is an R package for text analysis pre-processing that transforms numbers written in words to numeric digits (e.g., “one hundred and twenty three thousand” to “123000”). Works on numbers up to the decillions.

## Installation

You can install wordstonumbers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fsingletonthorn/words_to_numbers")
```

## Example

The words_to_numbers function deals with the most common ways that numbers are reported as words. For example:

```{r example1}
library(wordstonumbers)

words_to_numbers("ninety-nine red balloons")
```

```{r example2}

words_to_numbers("The answer is forty-two")
```

```{r example3}

words_to_numbers("The PRQ is a twelve-item, four-point Likert scale (from one = Never to four = Very Often) with three sub-scores.")
```

```{r example4}
words_to_numbers("The Library of Babel (by Jorge Luis Borges) describes a library that contains all possible four-hundred and ten page books made with a character set of twenty five characters (twenty two letters, as well as spaces, periods, and commas), with eighty lines per book and forty characters per line.")
```

This function attempts to break numbers apart 'intelligently', guessing which values are likely to represent separate numbers, e.g.:

```{r example9}
words_to_numbers("one two three four")
```

```{r example10}
words_to_numbers("one hundred and seventeen one hundred")
```

The function can also deal with some common cases where non-decimal numeric digits are intersperced with numbers-as-words. 

```{r example8}
words_to_numbers("three hundred billion, two hundred and 79 cats")

words_to_numbers("300 billion, 2 hundred and 79 dogs")

words_to_numbers("17 hundred freshwater fish")
```

## Limitations

However, not all ways that numbers can reported in text are correctly transformed at the moment. 

For example, this function does not currently correctly process magnitudes preceded by decimals, e.g.:

```{r example6}
words_to_numbers("1.6 Billion")
```

It also only breaks apart values after decimals using the same rules as for normal numbers, meaning that if people list numbers after decimals they will be read as separate values.

```{r example7}
words_to_numbers('three point one four one five nine two six')
```

It also does not yet recognise that certain numbers are likely to represent years.

```{r example11}
words_to_numbers('nineteen twenty')
```

Please report any bugs or issues [here](https://github.com/fsingletonthorn/words_to_numbers/issues)!

